Drug sensitivity prediction with the normal inverse Gaussian prior informed by external data

### 2019-11-27 docs/biometrical_main.Rnw
git before old checkout

  %% Authors
  \author[M\"unch]{Magnus M. M\"unch
  \footnote{Corresponding author: {\sf{e-mail: m.munch@amsterdamumc.nl}}, 
  Phone: +31 71 527 4844}\inst{,1,2}} 
  \author[van de Wiel]{Mark A. van de Wiel\inst{1,3}}
  \author[Richardson]{Sylvia Richardson\inst{3}}
  \author[Leday]{Gwena{\"e}l G. R. Leday\inst{3}}

@@

	\section*{Acknowledgements}

>>>>

  %% Authors
  \author[M\"unch]{Magnus M. M\"unch
  \footnote{Corresponding author: {\sf{e-mail: m.munch@amsterdamumc.nl}}, 
  Phone: +31 71 527 4844}\inst{,1,2,3}} 
  \author[van de Wiel]{Mark A. van de Wiel\inst{1,3}}
  \author[Richardson]{Sylvia Richardson\inst{3}}
  \author[Leday]{Gwena{\"e}l G. R. Leday\inst{3}}

@@

	\section*{Acknowledgements}
	A visit of MM to SR and GL was funded by the Amsterdam Public Health 
	institute's Methodology travel grant.

### 2019-11-27 docs/manuscript1.Rnw
git before old checkout

% settings
\pgfplotsset{compat=1.16}
\graphicspath{{../figs/}}
\setlength{\evensidemargin}{.5cm} \setlength{\oddsidemargin}{.5cm}
\setlength{\textwidth}{15cm}
\title{Drug sensitivity prediction with the normal inverse Gaussian prior 
informed by external data}
\date{\today}
\author{Magnus M. M\"unch$^{1,2}$\footnote{Correspondence to: 
\href{mailto:m.munch@amsterdamumc.nl}{m.munch@amsterdamumc.nl}}, Mark A. van de 
Wiel$^{1,3}$, Sylvia Richardson$^{3}$, \\ and Gwena{\"e}l G. R. Leday$^{3}$}

@@

	\section*{Acknowledgements}
	We thank Zhi Zhao and Leiv Tore Salte R{\o}nneberg from the Oslo Centre for 
	Biostatistics and Epidemiology for their suggestions on the pre-processing of 
	the GDSC data. \textit{Conflict of Interest}: None declared.

>>>>

% settings
\pgfplotsset{compat=1.16}
\graphicspath{{../figs/}}
\setlength{\evensidemargin}{.5cm} \setlength{\oddsidemargin}{.5cm}
\setlength{\textwidth}{15cm}
\title{Drug sensitivity prediction with the normal inverse Gaussian prior 
informed by external data}
\date{\today}
\author{Magnus M. M\"unch$^{1,2,3}$\footnote{Correspondence to: 
\href{mailto:m.munch@amsterdamumc.nl}{m.munch@amsterdamumc.nl}}, Mark A. van de 
Wiel$^{1,3}$, Sylvia Richardson$^{3}$, \\ and Gwena{\"e}l G. R. Leday$^{3}$}

@@

	\section*{Acknowledgements}
	% We thank Zhi Zhao and Leiv Tore Salte R{\o}nneberg from the Oslo Centre for 
	% Biostatistics and Epidemiology for their suggestions on the pre-processing of 
	% the GDSC data. 
	A visit of MM to SR and GL was funded by the Amsterdam Public Health 
	institute's Methodology travel grant.
	\textit{Conflict of Interest}: None declared.
